Comparing Early Evolution of Flames in X-ray Bursts in Two and Three Dimensions

### 2023-03-05 xrb3/paper.tex
turn on line numbers
a bit more code description

\documentclass[twocolumn,times,tighten]{aastex631}

@@

In \citet{eiden:2020}, we developed the simulation methodology in
\castro\ for modeling laterally spreading flames through the accreted
layer on the surface of a neutron star.  Building on this, in
\citet{harpole:2021}, we explored several different rotation rates and
initial model thermal structures to understand how the flame speed
depends on the thermal structure of the envelope.  Both of these
papers used a two-dimensional axisymmetric geometry.  The
three-dimensional simulations we present here build on these works.
We use a neutron star crust temperature of $2\times 10^8~\mathrm{K}$
and rotation rate of 1000~Hz, as followed in \citet{harpole:2021}.
This model was chosen here since it gives a clean well-defined flame.
The model is constructed following the same procedure described in
\citet{eiden:2020,harpole:2021}.

>>>>

\documentclass[twocolumn,linenumbers,times,tighten]{aastex631}

@@

In \citet{eiden:2020}, we developed the simulation methodology in
\castro\ for modeling laterally spreading flames through the accreted
layer on the surface of a neutron star.  For these models,
\castro\ evolves the compressible Euler equations with a Coriolis
force arising from rotation, constant gravity (the plane-parallel
approximation), reactive sources, and thermal diffusion (integrated
explicitly).  We use a general stellar equation of state with
radiation, ions as a perfect gas, and degenerate/relativistic
electrons described in \citet{timmes_swesty:2000}.  Building on these
first simulations, in \citet{harpole:2021}, we explored several
different rotation rates and initial model thermal structures to
understand how the flame speed depends on the thermal structure of the
envelope.  Both of these papers used a two-dimensional axisymmetric
geometry.  The three-dimensional simulations we present here build on
these works.  We use a neutron star crust temperature of $2\times
10^8~\mathrm{K}$ and rotation rate of 1000~Hz, as followed in
\citet{harpole:2021}.  This model was chosen here since it gives a
clean well-defined flame.  The model is constructed following the same
procedure described in \citet{eiden:2020,harpole:2021}.
